### 2021-10-28 src-latex/parts/00-abstract.tex
Suggestion of structure

% !TeX root = ../main-paper.tex
The paper features a comparison of a selection of named entity recognition (NER) techniques which can be reasonably used in the context of historical document analysis.
Such natural language processing techniques identify which class each text token belong to, like "person name", "location", "number" or "activity".
Introducing a new public dataset built from 19th century French directories, 
we perform a practical assessment of the accuracy of, and the annotation cost (considering various training set sizes) needed by each technique.
We also study the impact of real OCR noise for several OCR systems on the performance of NER.
Experiments suggest that FIXME APPROACH NAME is the most effective approach on the dataset we processed.
All material is available freely at \url{https://github.com/soduco/paper-ner-bench-das22} and the latest version of is paper can be obtained at \url{TODO arxiv URL}.

>>>>

% !TeX root = ../main-paper.tex
The paper features a comparison of a selection (FIXME be more specific/enumerate) of named entity recognition (NER) techniques which can be reasonably used in the context of historical document analysis.
Such natural language processing techniques identify which class each text token belong to, like "person name", "location", "number" or "activity".
Introducing a new public dataset built from 19th century French directories, 
we perform a practical assessment of the accuracy of, and the annotation cost (considering various training set sizes) needed by each technique.
We also study the impact of real OCR noise for several OCR systems on the performance of NER.
Experiments suggest that FIXME APPROACH NAME is the most effective approach on the dataset we processed.
FIXME add numerical results
Results can be reproduced using data and code freely available at \url{https://github.com/soduco/paper-ner-bench-das22}
and the latest version of is paper can be obtained at \url{TODO arxiv URL}.

### 2021-10-28 src-latex/parts/10-introduction.tex
Suggestion of structure

>>>>

\textbf{TODO sample (simplified) pipeline of the information extraction process}
\textbf{and/or}
\textbf{TODO illustration a sample page (full image, large crop, entry crop with highlighted entities)}

% General context + scope limitation
NER is a fundamental step of the information extraction pipeline when processing historical listing, like directories for instance.
OCRed text is not sufficient to build a high level, semantic view of the collection under study;
indeed, being able to properly tag text tokens unlocks the ability to relate entities,
and provide colleagues from digital humanities with useful databases.

% Problematic
NER requires training data, and we have little training data for historical documents.
OCR is also noisy.
How can we extract reliable elements in this context?

% Contributions
\begin{enumerate}
    \item review state of the art regarding NER for historical documents (section 2)
    \item dataset (section 3)
    \item list usable techniques (more to evangelize the DAR community) (section 4)
    \item compare their performance under various training set sizes (thus annotation costs) and OCR noise levels (thus OCR choices/luck/availability) (sec. 5 and 6)
    \item suggest smart way to leverage side knowledge like lexicons (FIXME iif this works well, maybe a conclusion instead)
\end{enumerate}

### 2021-10-28 src-latex/parts/30-dataset.tex
Setup paper structure
Suggestion of structure

% !TeX root = ../main-paper.tex
\section{Related Work}

>>>>

% !TeX root = ../main-paper.tex
\section{Dataset}

TODO interesting points to detail:
\begin{itemize}
    \item origin
    \item illustration (maybe in first figure)
    \item various numbers (of original data and of the sample we extracted)
    \item statistics about entry lengths (histogram of number of char / tokens par entry)
    \item entities we considered and how we annotated them (how we assessed gold's quality)
    \item OCR data (automated systems and clean text + how we created the "clean" text + whether/how we assessed clean text's quality)
    \item \dots
\end{itemize}

### 2021-10-28 src-latex/parts/40-ner-approaches.tex
Setup paper structure
Suggestion of structure

% !TeX root = ../main-paper.tex
\section{Dataset}

>>>>

% !TeX root = ../main-paper.tex
\section{NER Approaches}

TODO describe
\begin{itemize}
    \item regexp
    \item spacy cnn
    \item spacy cnn + lexicon (warning: how do we build it?)
    \item transformer
\end{itemize}

% Other possibilities:
1. Traditional ML based:

    Conditional Random Fields (CRF) - https://pypi.org/project/sklearn-crfsuite/
    Maximum-entropy Markov model

2. Neural Networks based:

    LSTMs, bi-LSTM - https://github.com/flairNLP/flair
    CNNs (SpaCy uses CNN based architecture)
    Transformers (Spacy has recently launched it) - https://spacy.io/universe/project/spacy-transformers

### 2021-10-28 src-latex/parts/50-xp-setup.tex
Suggestion of structure

\subsection{Implementation details}
we use spacy \mcite{spacy}

>>>>

\subsection{Metrics}
\begin{itemize}
    \item NER quality: accuracy? precision? recall? f-score? (idea: stick with standard spacy/sklearn metrics)
    \item OCR accuracy: outputs from standard tools (beware of unknown glyphs: do we need any special care?)
\end{itemize}

\subsection{Training procedure}
train/val/test splits, number of runs, etc.

\subsection{Parameters for each method}

\subsection{Implementation details}
we use spacy \mcite{spacy}
will we use FLAIR as well?

### 2021-10-28 src-latex/parts/60-results.tex
Setup paper structure
Suggestion of structure

% !TeX root = ../main-paper.tex
\section{Experimental Setup}

\subsection{Implementation details}
we use spacy \mcite{spacy}

>>>>

% !TeX root = ../main-paper.tex
\section{Results}

\subsection{Experiment 1: Accuracy vs NER approach vs training set size}

Qualitative results
\textbf{TODO random samples of results + selection of failure cases}

Quantitative results: table + graph ideally (with training set size info)

\begin{verbatim}
Accuracy
|                             ..o   
|                ..o       o/       
|            ./`          /`          
|        ./o`      .o   o            
|     ./`        .`                    One curve per approach
|    o       o/`                  o  
|          .`                  ./    
|       o`                    /      
|                         .o        
|                       .`           
|                      o            
|                                   
+------------------------------   Training set size
\end{verbatim}

\subsection{Experiment 2: Accuracy vs NER approach vs OCR noise}

Qualitative results
\textbf{TODO random samples of results + selection of failure cases}

Quantitative results: table + graph ideally (with OCR noise, same format as previous)

Opt. use synthetic text perturbation as well? Maybe not interesting and too artificial if we have access to 2+ OCR systems.
(original OCR from BNF, Tesseract 4, Pero OCR…)

\subsection{Discussion}
Interesting points to discuss:
\begin{itemize}
    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
    \item Construction of the lexicon and associated cost
\end{itemize}
